---
title: "SQLandR"
output:
   html_document:
      self_contained: false
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	echo = TRUE,
	message = FALSE,
	warning = FALSE
)
```


loading the SQLLite db file into R

```{r echo=TRUE, paged.print=TRUE}
library(RSQLite)

filename <- "advert.db"
sqlite.driver <- dbDriver("SQLite")
db <- dbConnect(sqlite.driver,
                dbname = filename)

```

List the tables avalaible in the db

```{r echo=TRUE, paged.print=TRUE}
dbListTables(db)
```

passing the "campaings" db table in a R dataframe named **campaignsinfo** and listing the data

```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}

campaingnsinfo<-dbReadTable(db, "campaigns")
knitr::kable(campaingnsinfo)

```

df constists of 11 observations of 3 variables(`ID`,`PAYOUT`, `ACCOUNT_MANAGER`) we will change the name of the `ID` variable to `CAMPAiNGID` since ID is used also as a variable name in the conversions datasets

```{r echo=TRUE, warning=FALSE, paged.print=TRUE}
library(dplyr)
campaingnsinfo<-campaingnsinfo%>%rename(CAMPAIGNID=ID)
knitr::kable(head(campaingnsinfo, n=11))
```

Merging the indivudal csv files containing the conversion events from 01-03-2019 to 07-03-2019 to a dataframe naned **conversionevents**


```{r echo=TRUE, message=FALSE, warning=FALSE}
#change the wd to the folder where conversion files stored
setwd("/Users/christospsaropoulos/Documents/Git/SQLandR/conversions")
getwd()
library(stringr)
library(readr)
library(purrr)
library(dplyr)

#create a list with the names of the csvs that contain the conversion data
files <- list.files( pattern = "csv", full.names = TRUE)
#merge the individual csv adding a column that contains the file name 
conversionevents<-files %>% 
  map(.f = ~read_csv(.x)) %>%
  set_names(nm = files) %>%     
  map_dfr(identity, .id = "Name")
#replace the Name column with Date
conversionevents<-conversionevents%>%mutate(Name=str_extract(Name,"[0-9]{4}[-][0-9]{2}[-][0-9]{2}+"))%>%rename(Date=Name)%>%mutate(Date=as.Date(Date))
conversionevents
```

Removing duplicates from the **conversionevents** dataframe and saving the unique values in a new dataframe named **conversionevents_unique**. 
A total of 2389 duplicate values have been removed.

```{r echo=TRUE}
conversionevents_unique<-distinct(conversionevents)
conversionevents_unique

```

Loading the rejected conversions in a R dataframe named **rejections**. As we can see we have 4779 rejected conversions

```{r echo=TRUE}

rejections <- read.table("rejections.txt", header=FALSE, fill = TRUE)
rejections<-rejections%>% mutate_all(as.character)%>%rename(ID=V1)
head(rejections)
summary(rejections)

```


excluding `ID`listed in **rejections** from **conversionsevents_unique**

```{r echo=TRUE}
conversionevents_unique<-conversionevents_unique %>% anti_join(rejections)
conversionevents_unique
```

Grouping conversions per `GAMPAINGID`

```{r echo=TRUE}
conversionevents_unique %>% group_by(CAMPAIGNID) %>%summarise( campaignconversion = n())
```

Joining the **conversionevents_unique** dataframe with the **campaigninfo** dataframe in a dataframe named **master**

```{r echo=TRUE}
master<-full_join(conversionevents_unique,campaingnsinfo,by="CAMPAIGNID")
master
```

calculating spend per campaign

```{r echo=TRUE, paged.print=TRUE}
master2<-master%>% group_by(CAMPAIGNID,PAYOUT,ACCOUNT_MANAGER) %>%summarise( CAMPAIGN_CONVERSION = n())%>% mutate(TOTALSPEND=(PAYOUT*CAMPAIGN_CONVERSION))
knitr::kable(master2,n=11)
```

Selecting the column needed for Task1 Report

```{r echo=TRUE, paged.print=TRUE}
Task1<-master2%>%ungroup()%>%select(CAMPAIGNID,ACCOUNT_MANAGER,CAMPAIGN_CONVERSION,PAYOUT,TOTALSPEND)
knitr::kable(Task1, n=11)
```

calculating daily spend per campaign

```{r echo=TRUE, paged.print=TRUE}
master3<-master%>% group_by(CAMPAIGNID,Date,PAYOUT) %>%summarise( CAMPAIGN_CONVERSION = n())%>% mutate(TOTALSPEND=(PAYOUT*CAMPAIGN_CONVERSION))
master3

```
calculating daily percentage differences per campaign
```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}
library(scales)
dailydiff<-master3%>%ungroup()%>%select(Date,CAMPAIGNID,TOTALSPEND)%>%group_by(CAMPAIGNID,Date)%>%summarise(TOTALSPEND = sum(TOTALSPEND))%>% mutate(DIFF=TOTALSPEND-lag(TOTALSPEND, n=1),PERCENT_DIFF = percent(DIFF/lag(TOTALSPEND,n=1)))
dailydiff

```
Selecting the column needed for Task2 Report
```{r}
Task2<-dailydiff%>%ungroup()
Task2
```

Exporting Task1 and Task2 Report in an xlsx file


```{r echo=TRUE, message=FALSE, warning=FALSE, paged.print=TRUE}

library(xlsx)

# create new workbook
wb <- createWorkbook()

#--------------------
# DEFINE CELL STYLES 
#--------------------
# title and subtitle styles
title_style <- CellStyle(wb) + 
               Font(wb, heightInPoints = 16,
                    color = "blue", 
                    isBold = TRUE, 
                    underline = 1)

subtitle_style <- CellStyle(wb) + 
                  Font(wb, heightInPoints = 14,
                       isItalic = TRUE,
                       isBold = FALSE)

# data table styles
rowname_style <- CellStyle(wb) +
                 Font(wb, isBold = TRUE)

colname_style <- CellStyle(wb) +
                 Font(wb, isBold = TRUE) +
                 Alignment(wrapText = TRUE, horizontal = "ALIGN_CENTER") +
                 Border(color = "black",
                        position = c("TOP", "BOTTOM"),
                        pen = c("BORDER_THIN", "BORDER_THICK"))



#-------------------------
# CREATE & EDIT WORKSHEET 
#-------------------------
# create worksheets
sheet1 <- createSheet(wb, sheetName = "Task1")
sheet2 <- createSheet(wb, sheetName = "Task2")

# helper function to add titles
xlsx.addTitle <- function(sheet, rowIndex, title, titleStyle) {
        rows <- createRow(sheet, rowIndex = rowIndex)
        sheetTitle <- createCell(rows, colIndex = 1)
        setCellValue(sheetTitle[[1,1]], title)
        setCellStyle(sheetTitle[[1,1]], titleStyle)
}

# add title and sub title to worksheet
xlsx.addTitle(sheet = sheet1, rowIndex = 1, 
              title = "Advert",
              titleStyle = title_style)

xlsx.addTitle(sheet = sheet2, rowIndex = 1, 
              title = "Advert",
              titleStyle = title_style)

xlsx.addTitle(sheet =sheet1, rowIndex = 2, 
              title = "Total Spend per Campaign & Account Manager",
              titleStyle = subtitle_style)

xlsx.addTitle(sheet =sheet2, rowIndex = 2, 
              title = "Total Spend per Campaign & Account Manager Declining Campaigns",titleStyle = subtitle_style)

# add data frame to worksheet
addDataFrame(Task1, sheet = sheet1, startRow = 3, startColumn = 1,
             colnamesStyle = colname_style, 
             rownamesStyle = rowname_style)

addDataFrame(Task2, sheet = sheet2, startRow = 3, startColumn = 1,
             colnamesStyle = colname_style, 
             rownamesStyle = rowname_style)

# change row name column width
setColumnWidth(sheet = sheet1, colIndex = 1, colWidth = 3)
setColumnWidth(sheet = sheet1, colIndex = 2, colWidth = 38)
setColumnWidth(sheet = sheet1, colIndex = 3, colWidth = 21)
setColumnWidth(sheet = sheet1, colIndex = 4, colWidth = 15)

# change row name column width
setColumnWidth(sheet = sheet2, colIndex = 1, colWidth = 3)
setColumnWidth(sheet = sheet2, colIndex = 2, colWidth = 38)
setColumnWidth(sheet = sheet2, colIndex = 3, colWidth = 25)
setColumnWidth(sheet = sheet2, colIndex = 4, colWidth = 30)


# save workbook
saveWorkbook(wb, file = "AdvertReport.xlsx")

# view the file
#library(r2excel)
#in case you do not have r2excel package in  your library please run the following: 
#install.packages("devtools")
#devtools::install_github("kassambara/r2excel")
#xlsx.openFile("BlueBananaReport.xlsx")
```




